FinalManuscript_DISCS_UG

### 2018-07-15 parts/01_introduction_04significanceofstudy.tex
Revised 2.1

The results of the study will provide

>>>>

This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption \cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, support for more complicated image processing operations such as image convolution must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature \cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.

We wish to contribute to existing models for the secure transmission and modification of image data by developing a software library which allows the use and comparison of various homomorphic encryption algorithms. Our software library would allow service providers to perform image manipulation for clients without compromising data privacy.

### 2018-07-15 parts/02_relatedliterature.tex
Revised 2.1

\section{Homomorphic Cryptosystems}
% [include mention of metrics by which they are compared]

In cryptography, a cryptosystem consists of an encryption function $\mathcal{E}$ and a decryption function $\mathcal{D}$, along with the plaintext space $\mathcal{P}$, ciphertext space $\mathcal{C}$ and the key space $\mathcal{K}$~\cite{bauer_cryptosystem_2005}. A \textit{plaintext} is text that can be easily understood by everybody. On the other hand, a \textit{ciphertext} is a result from encrypting the plaintext using an encryption key. The \textit{plaintext space} is the set of all possible plaintexts, the \textit{ciphertext space} is the set of all possible ciphertexts, while the \textit{keyspace} consists of all possible keys.

There are two kinds of cryptosystems, namely: \textit{symmetric} and \textit{asymmetric}. In symmetric-key cryptosystems, the same key is used for both encryption and decryption. As a consequence, the encryption and decryption functions are inverses of each other. Prominent examples of symmetric-key cryptosystems are the Data Encryption Standard (DES), and its replacement, the Advanced Encryption Standard (AES).

On the other hand, asymmetric-key (or public-key) cryptosystems use separate keys for encryption and decryption. The encryption key (also called the \textit{public key}) is shared to everybody, while the decryption key (also called the \textit{private key}) is kept secret. Because of this, there is no need to agree upon some secure key sharing protocols. Usually, the security of asymmetric-key cryptosystems relies on the intractability of certain computational problems, like how RSA depends on the difficulty of integer factorization \cite{rivest_method_1978}, while ElGamal depends on the difficulty of the discrete logarithm problem \cite{blakley_public_1985}.

Homomorphic cryptosystems are a special type of cryptosystem wherein operations can be securely performed on encrypted data. Suppose that for a public-key cryptosystem, $\mathcal{E}_k \left(p \right)$ is the encryption function using the public key $k \in \mathcal{K}$, and $\mathcal{D}_l \left(c \right)$ be the decryption function using the private key $l$. A cryptosystem is said to be homomorphic if its encryption function is homomorphic, that is, if it satisfies the relation
\begin{equation}
    \mathcal{E}_k \left(p_1 \boxplus p_2\right) = \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right)
\end{equation}
where $p_1, p_2 \in \mathcal{P}$ are the plaintexts, and $\boxplus$ and $\oplus$ are operations in $\mathcal{P}$ and $\mathcal{C}$ respectively \cite{fontaine_survey_2007}. Furthermore, a homomorphic cryptosystem also satisfies \cite{li_elliptic_2012}
\begin{equation}
    p_1 \boxplus p_2 = \mathcal{D}_l \left( \mathcal{E}_k \left(p_1\right) \oplus \mathcal{E}_k \left(p_2\right) \right).
\end{equation}
In other words, a homomorphic cryptosystem preserves the operations that can be typically done with the plaintext without the intermediary step of decrypting the ciphertext beforehand. An important note about the defintion of a homomorphic cryptosystem is that the operations $\boxplus$ and $\oplus$ need not be the same. A simple operation in the plaintext space may require a computationally intensive operation in the ciphertext space.

Homomorphic cryptosystems are classified according to the plaintext and ciphertext operations, $\boxplus$ and $\oplus$. If the plaintext operation $\boxplus$ is addition, the cryptosystem is said to be \textit{additively homomorphic}, and the cryptosystem is said to be \textit{multiplicatively homomorphic} if the plaintext operation $\boxplus$ is multiplication. Some examples of homomorphic cryptosystems include the Goldwasser-Micali cryptosystem \cite{goldwasser_probabilistic_1984} and the Paillier cryptosystem \cite{stern_public-key_1999}. Even some classic public-key cryptosystems are homomorphic, both RSA and ElGamal are multiplicatively homomorphic, while elliptic curve cryptosystems are additively homomorphic \cite{li_elliptic_2012}. These cryptosystems, while relatively efficient, only support a limited set of operations on the encrypted data.

However, there exists \textit{fully homomorphic} cryptosystems, where instead of being limited to operations like addition or multiplication, it allows any arbitrary operations on the ciphertext. It is only in recent years that a fully homomorphic cryptosystem has been described. Gentry's cryptosystem, which uses lattice-based cryptography, allows arbitrary functions that are constructed from various addition and multiplication operations \cite{gentry_fully_2009}. Gentry's cryptosystem allows for the computation of arbitrary Boolean circuits on binary data. While improvements have been developed for Gentry's original scheme \cite{hutchison_fully_2010, sen_homomorphic_2013}, since the homomorphic property of these systems is applied on each bit of the plaintext/ciphertext elementary addition and multiplication operations on the plaintext are compuationally intensive \cite{sen_homomorphic_2013, shortell_secure_2016}.

>>>>

\input{parts/02_relatedliterature_01homomorphiccryptosystems}
